---
title: "Stat 850 Project Description"
author: "Alyssa Grube, Kultjit Bhatti, Rene Ingersoll"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
```

```{r load-sas-libraries, echo = F, message = F, warning = F}

library(SASmarkdown)
sas_enginesetup(sashtml=sashtml)

sasexe <- "C:/Program Files/SASHome/SASFoundation/9.4/sas.exe"
sasopts <- "-nosplash -ls 75"

# Linux options (for grading, please leave this in!)
# sasexe <- "/usr/local/SASHome/SASFoundation/9.4/bin/sas_en"
# sasopts <- "-ls 75"
```


## Instructions
  
Each member of your team should modify this document in some way and push their modifications to the repository in a separate commit. This will ensure that you have set your repository up so that all group members are working with the same repository. 

Note that you must compile your readme (this document) for it to properly display as part of your github repository. 

Once you have received feedback on your project proposal (via Canvas) you may alter this README so that it describes your final project instead of the project proposal. 

## Data Set
Provide a link to your dataset here, and a description of the variables in the data set.
https://www.ers.usda.gov/data-products/food-environment-atlas/data-access-and-documentation-downloads/
The above is the link to the dataset we are using.

#List of variables of interest:  

Diabetes: PCT_DIABETES_ADULTS13 

 * adult diabetes rate 

Obesity: PCT_OBESE_ADULTS17  

 * adult obesity rate  

Students eligible for free lunch/ reduced lunch/Breakfast and summer programs: PCT_FREE_LUNCH15, PCT_SBP17, and PCT_SFSP17 

 * these variables can provide an idea of children's access to food, usually     students are placed on these school programs if they do not have access at home 

Low access: LACCESS_POP15, LACCESS_LOWI15, LACCESS_HHNV15 

 * data provides a couple of variations on this data, such as the base population, those with low income, households with no car, and based on demographics (ie: age and ethnicity) 

Recreational Centers: RECFACPTH16 

 * the data provides a sum of recreation and fitness facilities within each county 

**Note**: the variables listed above are a tentative selection to use in our project, the data is presented with observations from multiple years as well as based on different demographics, therefore, as we explore the data more, our list of variables may change as we explore comparisons between age, ethnicity, difference between years, etc. These will be used to determine what additional variables should be explored in order to draw conclusions from the data and observe patterns. 

#Files to use:
1.  VariableList.csv 
  * this includes description of all the variables in the Food Environment Atlas, organizing them by category (Access, Demographics, Health, etc.), the variable code used in the associated files and the units which the data is provided in
    
2.  StateAndCountyData.csv
    *  contains data for each variable by County and State, it is organized by category listed for the variable in VariableList.cvs
    

## Potential Topics to Explore Using the Data Set
Describe avenues you might explore using the data. 
* We would like to explore rates of diabetes and obesity to see how they correlate to data regarding food availability and recreational facilities in the United States. 

What are your goals? 
* Our goals are to see if there are any patterns in public health and access to food and the correlation between recreational facilities and obesity across various communities and regions. 

How do you plan to explore the data? 
* The R programming language will be used in order to filter, sort, and plot the data into interpretative graphs, tables, and maps in order to observe any trends and correlations in these trends. Exploratory figures will be created in our initial variables we want to explore; these will be used to extrapolate and determine what other variables should be inspected using R programming. 


You can provide some exploratory plots here if you have them available, otherwise, list what types of things you will be looking for.
* We plan to look at the difference in the variables of interest at varying geographic locations in the United States. Also, we are interested if local culture, specifically people's ability and willingness to travel or access recreational facilities and food, plays a part on people's health.  Lastly, we are curious if these differences are region specific, such as do they vary from east coast, Midwest, west coast, and rural to urban.


## Group Members
* Alyssa Grube
* Kuljit Bhatti
* Rene Ingersoll

