---
title: "Workspace"
author: "Rene, Alyssa, Kuljit"
date: "11/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Variables:
PCT_OBESE_ADULTS17-> Obesity rate 2017
RECFACPTH16-> /1000 population
RECFAC16-> Count
PCH_RECFAC_11_16-> %change from 2011 to 2016

RW<- ggplot(health, aes(x=PCT_OBESE_ADULTS17, y=PCH_RECFAC_11_16, color=County)) +
    geom_point()
Idea2<-ggplot(health1,aes(y=County))+
geom_segment(aes(x=PCT_OBESE_ADULTS12, xend=PCT_OBESE_ADULTS17, yend=County))+
geom_point(aes(x=PCT_OBESE_ADULTS12,color="PCT_OBESE_ADULTS12"))+
geom_point(aes(x=PCT_OBESE_ADULTS17,color="PCT_OBESE_ADULTS17"))

```{r Kuljit}
health<-read.csv("Health.csv")
library(dplyr)
library(ggplot2)
summary(health)
#obesity2017<-select(health,c('PCT_OBESE_ADULTS17'))
health1<-health[140:147,]
p <- ggplot(health, aes(x=PCT_OBESE_ADULTS17, y=PCH_RECFAC_11_16, color=State)) +
    geom_point()
Idea2<-ggplot(health1,aes(y=County))+
     geom_segment(aes(x=PCT_OBESE_ADULTS12, xend=PCT_OBESE_ADULTS17, yend=County))+
     geom_point(aes(x=PCT_OBESE_ADULTS12,color="PCT_OBESE_ADULTS12"))+
     geom_point(aes(x=PCT_OBESE_ADULTS17,color="PCT_OBESE_ADULTS17"))
Idea2

```


You can also embed plots, for example:

```{r Alyssa}

```

Testing....

```{r Rene}

```

