---
title: "Workspace"
author: "Rene, Alyssa, Kuljit"
date: "11/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(skimr)
library(patchwork)
library(ggpubr)
health<-read.csv("Health2.csv")

```

## R Markdown
Variables:
PCT_OBESE_ADULTS12-> Obesity rate in 2012
PCT_OBESE_ADULTS17-> Obesity rate in 2017
RECFACPTH16-> Rec facilities/1000 population
RECFAC16-> Count of Rec facilities in 2016
PCH_RECFAC_11_16-> %change in number of Rec facilities in 2016 from 2011.
PCTCHGOBESITY-> %Change in obesity between 2012-2017||SELF-CREATED

```{r Kuljit}
library(ggplot2)
library(skimr)
library(patchwork)
library(ggpubr)
library(reshape2)
health<-read.csv("Health2.csv")

a<-aggregate(formula = PCT_OBESE_ADULTS12 ~ State, data = health, FUN = mean)
b<-aggregate(formula = PCT_OBESE_ADULTS17 ~ State, data = health, FUN = mean)
c<-aggregate(formula = PCH_RECFAC_11_16 ~ State, data = health, FUN = mean)
d<-aggregate(formula = PCTCHG_12_17 ~ State, data = health, FUN = mean)

healthdata<- data.frame(State=c$State,RECCHG=c$PCH_RECFAC_11_16,OBESE12=a$PCT_OBESE_ADULTS12, OBESE17=b$PCT_OBESE_ADULTS17,PCTCHGOBESITY=d$PCTCHG_12_17)
#IDEA OF PLOTTING PCTCHGOBESITY and RECCHG on y-axis
p1<-ggplot(data=healthdata,aes(x=State,y=PCTCHGOBESITY, color=PCTCHGOBESITY ))+
  geom_point()
p2<-ggplot(data=healthdata,aes(x=State,y=RECCHG, color=RECCHG ))+
  geom_point()
p3 <- ggplot()+
  geom_point(data=healthdata,aes(x=State, y=RECCHG, colour="red"))+
  geom_point(data=healthdata,aes(x=State, y=PCTCHGOBESITY, colour="blue"))
p4<-p3+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p4+labs(title = "%Change in Rec vs Obesity", x = "States", y = "% Change", color = "Legend Title\n") +
  scale_color_manual(labels = c("RECCHG", "PCTCHGOBESITY"), values = c("red", "blue"))
cor(healthdata$PCTCHGOBESITY,healthdata$RECCHG, method=c("pearson", "kendall", "spearman"))


```


You can also embed plots, for example:

```{r Alyssa}

```

- Basic analsis of data for variables kuljit looked at
- Will add some maps for it tonight


```{r Rene}
#introduction to data
skim(health)

head(health)

summary(health$RECFAC16)
summary(health$PCT_OBESE_ADULTS12)
summary(health$PCT_OBESE_ADULTS17)
# higher averages in 2017 then compared to 2012

summary(health$PCH_RECFAC_11_16)
#some of the data has NA's, how are we handling this?


```

